WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-24 article/Article.tex
fix some typo
darcs-hash:20060324161341-2fc9d-ff61171a134722adff2f3f4d7a5ed5eb955b82d3.gz

Some convenient functions are provided with the itk module. They all begin with a lower
case character to clearly show they are not part of ITK.
\begin{itemize}
  \item \verb$itk.image(object)$ try to return an image from the object given in
parameter. If the object is an image, it is returned without changes. If the object
is a filter, the object returned by \verb$GetOutput()$ metyhod is returned.
This function is used in most of the next functions to allow the user to
pass an image or a filter, and is available here for the same usage in some custom
fuctions.

@@

These macros often take an optional second parameter which is a "dimensionality
condition" to restrict the dimensions that theis filter will be instantiated
for. The condition can either be a single number indicating the one dimension
allowed, a list of dimensions that are allowed (either as a single \verb$-$delimited
string or just a set of separate parameters), or something of the form \verb$n+$
(where \verb$n$ is a number) indicating that instantiations are allowed for dimension
n and above.

@@

By default, those classes are not loaded in the \verb$itk$ module to avoid loading
all the \verb$vtk$ module while importing \verb$itk$. The command \verb$import itkvtk$
will load the module, and add the classes both in \verb$itkvtk$ and\verb$itk$ module.
The classes are then usable as the other itk classes.

>>>>

Some convenient functions are provided with the itk module. They all begin with a lower
case character to clearly show they are not part of ITK.
\begin{itemize}
  \item \verb$itk.image(object)$ try to return an image from the object given in
parameter. If the object is an image, it is returned without changes. If the object
is a filter, the object returned by \verb$GetOutput()$ method is returned.
This function is used in most of the next functions to allow the user to
pass an image or a filter, and is available here for the same usage in some custom
fuctions.

@@

These macros often take an optional second parameter which is a "dimensionality
condition" to restrict the dimensions that the filter will be instantiated
for. The condition can either be a single number indicating the one dimension
allowed, a list of dimensions that are allowed (either as a single \verb$-$delimited
string or just a set of separate parameters), or something of the form \verb$n+$
(where \verb$n$ is a number) indicating that instantiations are allowed for dimension
n and above.

@@

By default, those classes are not loaded in the \verb$itk$ module to avoid loading
all the \verb$vtk$ module while importing \verb$itk$. The command \verb$import itkvtk$
will load the module, and add the classes both in \verb$itkvtk$ and \verb$itk$ module.
The classes are then usable as the other itk classes.
